\section{Technical Resources}
    \subsection{Helpful Sites}
    \subsubsection{Official Django Documentation Site}
    \noindent The official documentation was a super useful site since it contained almost all the necessary information when dealing with the framework as well as adapting built in functions to an application. Django's site contains extensive information on each version that is released to the public and is based upon an open source community for package development which became extremely useful for our project.\\
    
    \subsubsection{Amazon Web Services Console and Documentation}
    \noindent Amazon Web Services was an essential site and service for our web application. Via Amazon's console and detailed guidelines we were able to utilize this service through Oregon State University for necessary development on our project such as implement CAS services to allow login with student and staff accounts. Amazon's detailed guides also provided us with quality information on creating an instance with their servers so that we could hit the ground running with our choice of operating systema long with dedicated memory and storage.\\
    
    \subsubsection{Stack Overflow Website}
    \noindent We would like to credit the website Stack Overflow since we consolidated a number of posts that dealt with web application development to handle numerous issues that others have faced in the past. Seeing previous suggestions, solutions, and advice provided us with numerous learning opportunities while solving issues that we faced during the development of our project. 
    
    \subsection{Helpful Personnel}
    \subsubsection{Justin Wolford}
    \noindent Our client Justin was a great resource to have for our project. He provided quick and effective communication with the team while also providing valuable feedback. Justin also helped point us in the right direction when questioning certain implementations. Justin was also essential in aiding us for contacting the OSU CAS team and providing resources to create an account with Amazon Web Services.\\
    
    \subsubsection{OSU CAS Team}
    \noindent The OSU CAS Team was a great team to work with as they provided fast communication in setting us up with a development server to utilize CAS into our web application. Integration was smooth and effective making for a very pleasurable experience.\\
    
    
    