\documentclass[draftclsnofoot,onecolumn]{IEEEtran}
\usepackage[utf8]{inputenc}

\title{Student Letter of Recommendation Management Site}
\author{CS461 - Fall 2018 \\ Matthew Kottre}

\begin{document}

\maketitle

\section{Abstract}
Letters of recommendation play a significant factor when applying for a job or internship, but the task of asking an instructor for a letter of recommendation is overly complicated and time consuming. There is a lot of room for mistakes that further slow the process. There should be a management website that makes the process easier for both the student and the instructor. It should handle everything from requesting a letter to submitting and downloading the finished letter in a central management portal.

\pagebreak

\section{Problem Statement}
\subsection{What is the Problem?}
A very important factor when applying for a job or internship is a letter of recommendation. Instructors are the most common people to write these. While letters of recommendation are important, the process between asking for one and receiving it is overly complicated and time consuming. The current process involves:
\begin{enumerate}
    \item The student asks an instructor for a letter of recommendation
    \item The instructor has to check their current workload such as how many other letters they have already committed to.
    \item The instructor will inform the student, likely through email, whether they can write the letter or not.
    \item The instructor asks for additional materials such as a list of accomplishments and experience.
    \item The student sends the materials to the instructor, again likely over email.
    \item The instructor must keep track of how many letters they have committed to writing and the date they need to finish them by.
    \item The instructor sends the finished letter to the student using email.
\end{enumerate}

This process involves a lot of back and forth over email. This is not only time consuming, but opens the door for more problems such as emails ending up in spam or not responding to them immediately. This takes even more time to resolve and involves sending more emails. There is ample room for improvement.

\subsection{What is the Solution?}
The solution is a central portal that streamlines the process from start to finish making it easier to manage for both students and instructors. The website will allow students to ask an instructor for a letter of recommendation. It will also allow students to see the workload of instructors to get an idea about whether they would be a good candidate to write a letter of recommendation in the time required. Students will also be able to upload any additional documents and materials that instructors would like to have. The instructors would have a single place where they can keep track of which students they have committed to writing a letter for and what date they will have to finish them by. The use of a single portal specifically designed for managing letter of recommendation requests cuts many unnecessary steps saving both the instructor and the student time.

\subsection{When will the project be finished?}
Unlike some more open-ended projects, this one has clear criteria making it simple to know when it has solved the problem and can be considered \textit{done}. The problem will be solved when there is a working website that handles all of the necessary steps for a student to receive a letter of recommendation from an instructor. Without getting into too much detail, the website will allow a student to request a letter from an instructor, see their workload, let the instructor see how many letters they have currently committed to writing as well as their due dates, and uploading and downloading of the finished letter.

\end{document}
